### 2023-11-06 manuscript/manuscript.Rmd
Include the standards mixture in the methods section

Two example sample matrices were used for assessing the molecular formula assignment approach. 
The first was human urine purchased from BioIVT (Catalog# HUMANURINEPNN, Lot# 0393918) and spiked with a diverse mixture of `r nrow(standards_compound_info)` chemical standards from a previously validated assay that included `r standards_compound_MFs` unique molecular formulas [@beckmann2020].
A full list of the names and InChI chemical identifiers of the spiked chemical standards can be found in Additional file 1.
The second was healthy leaf tissue samples collected from four ecotypes of the model grass species *Brachypodium distachyon* using the method described in @parker2008.
Further details of the sample collection and extraction are described in the Additional file 2.

@@

For each biological sample matrix, the input data for molecular formula assignment had undergone spectral processing and pre-treatment and consisted of a sample by *m/z* feature intensity matrix containing both positive and negative ionisation mode data. 
Molecular formula assignment was conducted using the R package *assignments* v`r packageVersion('assignments')` and the approach comprised four major steps which are outlined in Figure \@ref(fig:figure-1-approach).
Where assignment was possible, *m/z* features were designated with unambiguous molecular formulas, isotopes and ionisation adduct assignments. 
The following sections outline the methodology behind each major step of the approach.

>>>>

Three example sample matrices were used for assessing the molecular formula assignment approach. 
The first was a diverse mixture of `r nrow(standards_compound_info)` chemical standards from a previously validated assay that included `r standards_compound_MFs` unique molecular formulas [@beckmann2020].
A full list of the names and InChI chemical identifiers of the chemical standards can be found in Additional file 1.
The second was human urine purchased from BioIVT (Catalog# HUMANURINEPNN, Lot# 0393918) and spiked with the sample mixture of chemical standards as used above.
The third was healthy leaf tissue samples collected from four ecotypes of the model grass species *Brachypodium distachyon* using the method described in @parker2008.
Further details of the sample collection and extraction are described in the Additional file 2.

@@

For each sample matrix, the input data for molecular formula assignment had undergone spectral processing and pre-treatment and consisted of a sample by *m/z* feature intensity matrix containing both positive and negative ionisation mode data. 
Molecular formula assignment was conducted using the R package *assignments* v`r packageVersion('assignments')` and the approach comprised four major steps which are outlined in Figure \@ref(fig:figure-1-approach).
Where assignment was possible, *m/z* features were designated with unambiguous molecular formulas, isotopes and ionisation adduct assignments. 
The following sections outline the methodology behind each major step of the approach.
